Analysis

### 2025-01-19 04-analisis.qmd
update corr tab and render paper

@fig-correlation presents a correlation matrix of the main variables analyzed, using data from the first wave. In this matrix, the correlations vary between low and moderate values. The correlations between justification of educational inequality with the two COVID variables are positive, but low. In addition, justification of education inequality depicts a moderate and negative association with the perception of inequality (_r_=-0.34, p<.01) and a moderate and positive association with both meritocracy perception variables (_r_=0.29, p<.01; _r_=0.24, p<.01). Regarding the perception of inequality, it presents a moderate and negative association with both meritocracy perception variables (_r_=-0.18, p<.01; _r_=-0.08, p<.01). Finally, the two meritocracy variables present a high and positive association with each other (_r_=0.76, p<.01).

>>>>

@fig-correlation presents a correlation matrix of the main variables analyzed, using data from the last wave (2023). In this matrix, the correlations vary between low and moderate values. The correlations between justification of educational inequality with the two COVID variables are positive, but low. In addition, justification of education inequality depicts a moderate and negative association with the perception of inequality (_r_=-0.28, p<.01) and a moderate and positive association with both meritocracy perception variables (_r_=0.17, p<.01; _r_=0.17, p<.01). Regarding the perception of inequality, it presents a moderate and negative association with both meritocracy perception variables (_r_=-0.19, p<.01; _r_=-0.14, p<.01). Finally, the two meritocracy variables present a high and positive association with each other (_r_=0.79, p<.01).

### 2025-01-19 production/prod_analysis-fix-t5.Rmd
update corr tab and render paper

```{r cor-plot, fig.dim=c(12,7)}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               sjPlot,
               sjmisc,
               summarytools,
               lavaan
               )
load(file = here::here("input/data-proc/df_study_t6_ind_comunas.RData"))
df_study1 <- df_study_long_t7_comunas %>% dplyr::select(idencuesta, ola, ponderador_long_total, segmento, estrato,
                                               just_educ, covid_economia, covid_beneficios, merit_talent, merit_effort, des_perc, 
                                               educ, ing_pc, ess, edad, sexo, pos_id) %>% na.omit()
# Full sample______________________________________________________________________
mat_full<- 
df_study1 %>%
   filter(ola==1) %>%
  select(just_educ, # distributive justice
         covid_economia,
         covid_beneficios,
         des_perc,
         merit_effort, merit_talent # meritocracy
         ) %>% 
  psych::mixedCor()

@@

from ELSOC 2016 (n = 1322)", x = 0.01, y = 0.05, just = "left", gp = grid::gpar(fontsize = 12, col = "black"))

>>>>

```{r cor-plot, fig.dim=c(12,7)}
rm(list=ls())
if (!require("pacman")) install.packages("pacman") # instalar pacman
                            # cargar librerias
pacman::p_load(dplyr,       # Manipulacion de datos
               knitr,
               kableExtra,
               sjPlot,
               sjmisc,
               summarytools,
               lavaan
               )
load(file = here::here("input/data-proc/df_study_t6_ind_comunas.RData"))
df_study1 <- df_study_long_t7_comunas %>% dplyr::select(idencuesta, ola, ponderador_long_total, segmento, estrato,
                                               just_educ, covid_economia, covid_beneficios, merit_talent, merit_effort, des_perc, 
                                               educ, ing_pc, ess, edad, sexo, pos_id) %>% na.omit()
# Full sample______________________________________________________________________
mat_full<- 
df_study1 %>%
   filter(ola==7) %>%
  select(just_educ, # distributive justice
         covid_economia,
         covid_beneficios,
         des_perc,
         merit_effort, merit_talent # meritocracy
         ) %>% 
  psych::mixedCor()

@@

from ELSOC 2023 (n = 1322)", x = 0.01, y = 0.05, just = "left", gp = grid::gpar(fontsize = 12, col = "black"))
